Ecological network control

### 2018-06-18 paper/supp-info.Rmd
All table labels must start with tab

We fitted the full set of possible candidate models and used the Akaike Information Criterion for small sample sizes (AICc) to compare the models. 
We found little support for any of the evaluated variables (Table \@ref(tab:table-controllabillity-model-results)). 
We measured the relative importance of an independent variable by adding the Akaike weights (the model probabilities) of the models in which the variable was present. 
All variables were roughly equally un-important with the Akaike weights for each of them ranging between `r round(min(controllability_variable_importance$w.plus), 3)` and `r round(max(controllability_variable_importance$w.plus), 3)` (in a scale from 0 to 1).

```{r table-controllabillity-model-results, results = "asis", sanitize = FALSE}
drake::loadd(controllability_models)

>>>>

```{r tab-controllabillity-model-results, results = "asis", sanitize = FALSE}
drake::loadd(controllability_models)
